Verifying Demonstrations

### 2018-11-27 paper/intro.tex
new, short abstract; adds explanation of protest as event instantiation

\emph{Context.} 
Consider the following scenario.
Alice is an activist that organizes a protest in some location(s) against the current government, represented by Grace.
On the one hand, Alice wants to estimate the number of participants to prove a certain support for her cause.
On the other hand, Grace is an autocratic regime leader who opposes Alice's cause.
Bob, Carol and many others participate in the protest for Alice's cause against Grace.
However, they might only be willing to do so in a manner that does not leave any digital traces because of the fear of retribution against them from Grace's regime. 
To realize this objective, a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved as of today.

>>>>

%\emph{Context.}

While our proposal is meant for crowd counting in general and to be applicable to any kind of event, we represent an event with a political protest against an oppressive regime throughout the paper. We choose this instantiation of an event because it is the most challenging in terms of requirements for privacy and verifiability (transparency).
Consider the following scenario.
Alice is an activist that organizes a protest in some location(s) against the current government, represented by Grace.
On the one hand, Alice wants to estimate the number of participants to prove a certain support for her cause.
On the other hand, Grace is an autocratic regime leader who opposes Alice's cause.
Bob, Carol and many others participate in the protest for Alice's cause against Grace.
However, they might only be willing to do so in a manner that does not leave any digital traces because of the fear of retribution against them from Grace's regime. 
To realize this objective, a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved as of today.
